---
title: "Recommendation Systems"
author: "Christian Urcuqui"
date: "2 de mayo de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## PCA Analysis

prcomp {stats} is the function to apply Principal Components Analysis 

```{r USAArests}

data("USArrests")

names(USArrests)

# lets see gow each variable is varying

apply(USArrests, 2, var)

# Murder    Assault   UrbanPop       Rape 
#  18.97047 6945.16571  209.51878   87.72916 

# so we see that the Assault is the most variable with variance

# it is important to apply a scalign process 

pca <- prcomp(USArrests, scale=TRUE)

names(pca)

# "sdev"     "rotation" "center"   "scale"    "x"       

# biplot is useful to know how the proportions of each variable along the two principal components

pca$rotation <- -pca$rotation
pca$x = -pca$x
biplot(pca,scale=0)

# from the biplot we can see that in PC1 and PC2, the variables Rape, Assault and Murder are more correlated than the UrbanPop feature. 


```

## Cluster Analysis 

Unsupervised techniques, we will apply KMeans 

```{r USAArests}

# K-means clustering

library(cluster)
data(iris)
iris$Species <-as.numeric(iris$Species)
kmeans <- kmeans(x=iris, centers = 5)
clusplot(iris,kmeans$cluster, color = TRUE, shade=TRUE, labels=13, lines=0)


# the k was selected by the elbow method

library(ggplot2)
cost_df <- data.frame()
for(i in 1:100)
{
  kmeans <- kmeans(x=iris, centers=i, iter.max=50)
  cost_df <- rbind(cost_df, cbind(i, kmeans$tot.withinss))
}
names(cost_df) <-c("cluster","cost")
#Elbow method to identify the idle number of clusters 
# Cost plot

ggplot (data =cost_df, aes(x=cluster, y=cost, group=1)) + 
  theme_bw(base_family = "Garamond") + 
  geom_line(colour= "darkgreen") +
  theme(text= element_text(size=20)) +
  ggtitle("Reduction in Cost For Values of 'k'\n") +
  xlab("\nClusters")


```
## Recommender Systems

So, it is important to know about the data we will use, because depends on it we can use four approaches, these are:

+ Collaborative filtering: information about similar items and users:
  + Item- based collaborative filtering: The recommendations are based on the most similar items that the user's purchases 
  + User-based collaborative filtering: This approach refers that the item recommendations are based on the most preferred by similar users. 
  
+ Content-based filtering: This is for each user; it defines a user profile through her/his history purchases and this technique

+ Hybrid filtering: This defines the recommendations using the above approaches 

+ Knowledge-based filtering: This uses explicit knowledge about the users and items 






## Bibliography

+ Building a Recommendation System with R. (2015). Gorakala, Suresh K., Usuelli, Michele

