---
title: "The mpg dataset"
author: "Christian Urcuqui"
date: "27 de febrero de 2018"
github: "urcuqui"
webpage: "urcuqui.github.com"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploratory dataset cars

We will use the packets provided in the tidyverse project in order to analyze the mpg dataset, this source has information of 30 car models and their features, such as, engine, year and hwy.


```{r cars}
library(tidyverse)
summary(mpg)
str(mpg)

```

## Including Plots

Ggplot is a special function to make a coordinate system whose allows us to add layers. These is the general template to make diagrams through ggplot:

ggplot(data= <DATA> ) + 
  <GEOM FUNCTION> mapping = aes (<MAPPING>)
  
ggplot(data= <Dataset> ) + 
  <funcion del grafico> mapping = aes (<mapeo de las variables>)  
  
First, we will use a scatter plot to analyze what is the data dispertion of some features. 

```{r first, echo=FALSE}

  ggplot(data=mpg) + 
    geom_point(mapping = aes(x=displ, y=hwy))

```

```{r other_Data, echo=FALSE}
# So, lets explore another dataset of cars
str(mtcars)

# We will make some scatterplots in order to show the importance to use nominal values and do not use categorical features. 

ggplot (data = mpg) + geom_point(mapping =aes(x=class, y=drv))

```
## Aesthehic Mappings

So, we can add other propierties in our graphics through the application of aesthethic (aes), this property allows us to add color, size and others to our points. The next code will add color by the categories in the feature class.

```{r explore_graphics, echo=FALSE}

ggplot(data=mpg) + 
  geom_point(mapping=aes(x=displ, y=hwy, color=class))

ggplot(data=mpg) + 
  geom_point(mapping = aes(x=displ, y=hwy, size=class))

ggplot(data=mpg) + 
  geom_point(mapping = aes(x=displ, y=hwy, alpha=class))

ggplot(data=mpg) + 
  geom_point(mapping = aes(x=displ, y=hwy, shape=class))

ggplot(data=mpg) + 
  geom_point(mapping=aes(x=displ, y=hwy), color="blue")

```
## Facets

This is another tool to split your visualization window in different parts, such as, the view can be divided by a categorical variable.

```{r facets, echo=FALSE}

ggplot(data=mpg) +
  geom_point(mapping=aes(x=displ, y=hwy)) +
  facet_wrap(~ class, nrow=2)

ggplot(data=mpg) +
  geom_point(mapping=aes(x=displ, y=hwy)) +
  facet_wrap(drv ~ cyl) 

ggplot(data=mpg) +
  geom_point(mapping=aes(x=displ, y=hwy)) +
  facet_grid(. ~ cyl) 

```

Facet exercises, we will explore what happen if we use some special features and combinations. 

```{r facetsother, echo=FALSE}
#1
ggplot(data=mpg) +
  geom_point(mapping=aes(x=displ, y=hwy)) +
  facet_grid(~displ)

#2
ggplot(data=mpg) +
  geom_point(mapping=aes(x=displ, y=hwy)) +
  facet_grid(drv ~ cyl)

ggplot(data=mpg) +
  geom_point(mapping=aes(x=drv, y=cyl))
    
#3
ggplot(data=mpg) +
  geom_point(mapping = aes(x =  displ, y=hwy)) +
  facet_grid(drv ~.)

ggplot(data=mpg) +
  geom_point(mapping=aes(x=displ, y=hwy)) +
  facet_grid(. ~ cyl) 

#4
ggplot(data =mpg) +
  geom_point(mapping=aes(x = displ, y=hwy)) +
  facet_wrap(~class, nrow=2)

#5
ggplot(data =mpg) +
  geom_point(mapping=aes(x = displ, y=hwy)) +
  facet_wrap(~class, ncol =2)


```

## Geometric Objetcs

Geom is an geometric object whose is used by a plot to represent the data.

```{r geometric, echo=FALSE}
ggplot(data=mpg) +
  geom_point(mapping = aes(x =displ, y=hwy))

ggplot(data=mpg) +
  geom_smooth(mapping = aes(x =displ, y=hwy, linetype=drv))

ggplot(data=mpg) +
  geom_smooth(mapping = aes(x =displ, y=hwy, linetype=drv, colour=drv))+
  geom_point(mapping = aes(x =displ, y=hwy, colour=drv))

ggplot(data = mpg) +
  geom_smooth(mapping=aes(x=displ, y=hwy))

ggplot(data = mpg) +
  geom_smooth(mapping=aes(x=displ, y=hwy, group=drv))

ggplot(data = mpg) +
  geom_smooth(mapping=aes(x=displ, y=hwy, group=drv, color=drv),
              show.legend = FALSE)

ggplot(data=mpg, mapping=aes(x =displ, y=hwy)) +
  geom_point(mapping = aes(colour=class)) +
  geom_smooth()

ggplot(data=mpg, mapping=aes(x=displ, y=hwy))+
  geom_point(mapping=aes(color=class))+
  geom_smooth(
    data=filter(mpg,class=="subcompact"),
    se=FALSE
  )


```

Exercices section 2
```{r excer2, echo=FALSE}

#1
#histogram

#2
#the next graphic integrates an scatter plot and geom_smooth without its confidence interval
ggplot(data=mpg, mapping = aes(displ, y=hwy, color=drv)) +
  geom_point()+
  geom_smooth(se=FALSE)

#3
#show.legend displays the information related to the graphic categories mapped in the plot

#4
#se argument in geom_smooth displays the confidence interval 

#5
#ggplot(data=mpg, mapping = aes(x =displ, ))

  




```


## Bar Graph

So, this section shows the use of bar charts in visual analysis. In this case, we will explore the diamonds dataset saved in ggplot2. Through this section you will see how edit the stat argument in order to show other views. 

```{r barGraph, echo=FALSE}
#which variables can we use?
str(diamonds)

ggplot(data = diamonds) +
  geom_bar(mapping = aes(x=cut))

#stat count is the default setting in geom_bar, so if we change it to the another one we will get the same result
ggplot(data = diamonds) +
  stat_count(mapping = aes(x=cut))

## So let's modify stat property.

demo <- tribble(
  ~a,     ~b,
  "bar_1", 20,
  "bar_2", 30,
  "bar_3", 40
)

# you can change the stat using the parameter stat and gives it identity 
ggplot(data=demo) +
geom_bar(
  mapping=aes(x=a, y=b), stat="identity"
)

# 
# ggplot(data=diamonds) +
#   geom_bar(
#     mapping= aes(x=cut, y= ..prob.., group=1)
#   )

# stat_summary is more flexible than stat_bin 
ggplot(data=diamonds) +
  stat_summary(
    mapping = aes(x=cut, y=depth),
    fun.ymin = min,
    fun.ymax = max,
    fun.y = median
  )
  


```

Exercies 3

```{r exer3, echo=FALSE}

#1. what is the default geom associated to stat_summmary? 
# the associated default geoms are geom_histogram/geom_freqpoly and stat_bin

ggplot(data=diamonds) +
  geom_histogram(mapping = aes(x=carat))

#2. what is the difference between geom_bar and geom_col
ggplot(data=diamonds) +
  geom_bar(mapping = aes(x=cut))

ggplot(data=diamonds) +
  geom_col(mapping = aes(cut,table))

# geom_col allows us to define the heights of the bars 

```
Let's see more bar charts with colors!

```{r bar2, echo=FALSE}

ggplot(data=diamonds) + 
  geom_bar(mapping=aes(x=cut, colour=cut))

ggplot(data=diamonds) + 
  geom_bar(mapping=aes(x=cut, fill=cut))

ggplot(data=diamonds) + 
  geom_bar(mapping=aes(x=cut, fill=clarity))

#what happen if we use position identity in the previous plot
ggplot(data=diamonds) + 
  geom_bar(mapping=aes(x=cut, fill=clarity), position="identity")
# the previous plot is not fine because some charts are overlapped, so, we need to change some aesthetic parameters
ggplot(data=diamonds,
       mapping=aes(x=cut, fill=clarity)) + 
  geom_bar(alpha=1/5, position="identity") 

ggplot(data=diamonds,
       mapping=aes(x=cut, color=clarity)) + 
  geom_bar(fill=NA, position="identity")



```
