---
title: "youtube-analytics"
author: "Christian Urcuqui"
date: "18 de septiembre de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analytics in youtube data

The next line codes explore some insights in the youtube data through the application of statistic and machine learning techniques 

```{r cars}
data <- read.csv(file.choose())
data_without_id <- data[,-c(1, 4)]
summary(data_without_id)


```

## Clean the data

Now we have the data that we want to analyze, but, what are the best registers for our propopuse?. Firstly, it is important to clean and get only the information without NAs.
The first hypothesis is what will happen if we use a median in suscriberCount and videoCount in order to replace the NA values 

```{r pressure, echo=FALSE}

data_NoNa <- data_without_id[is.na(data_without_id$viewCount)==FALSE,]
summary(data_NoNa)

data_Nona2 <- data_NoNa
data_Nona2[is.na(data_Nona2$subscriberCount),4] <- 938
data_Nona2[is.na(data_Nona2$videoCount),5] <- 59
summary(data_Nona2)

count.fields(data_Nona2[data_Nona2$viewCount!=0,])

```

```{r pressure, echo=FALSE}
library(Hmisc)
data_Nona2$videoCount <- as.integer(data_Nona2$videoCount)
data_Nona2$viewCount <- as.integer(data_Nona2$viewCount)
rcorr(data_Nona2[,c(5,6)], type="pearson") # type can be pearson or spearman

```
```{r pressure, echo=FALSE}
#install.packages("caret")
#install.packages("DAAG")
library(DAAG)
library(caret)
set.seed(1234)
partition <- createDataPartition(data_Nona2$viewCount, p=0.8, list=FALSE)
training <- data_Nona2[ partition, ]
testing <- data_Nona2[ -partition, ]
# Multiple Linear Regression
fit1 <- lm(formula = training$viewCount ~ training$dislikeCount + training$likeCount + 
       training$subscriberCount+ training$commentCount, data = training)
layout(matrix(c(1,2,3,4),2,2)) 
plot(fit1)




```
```{r pressure}

fit2 <- lm(training$viewCount ~ training$videoCount+ training$subscriberCount,data=training)
layout(matrix(c(1,2,3,4),2,2)) 
plot(fit2)


anova(fit1, fit2)
summary(fit2)

```

## Selection of the best characteristics for the last experiment

According to the Residual standard error, a regular model can be created with only two characteristics, but, it is not a good result because its value is 0.1226 

```{r pressure}

data_Nona3 <- data_NoNa
data_Nona3[is.na(data_Nona3$subscriberCount),4] <- 0
data_Nona3[is.na(data_Nona3$videoCount),5] <- 0
data_Nona3[is.na(data_Nona3$commentCount),1] <- 0
data_Nona3[is.na(data_Nona3$dislikeCount),2] <- 0
data_Nona3[is.na(data_Nona3$likeCount),3] <- 0

summary(data_Nona3)

data_Nona3$videoCount <- as.integer(data_Nona3$videoCount)
data_Nona3$viewCount <- as.integer(data_Nona3$viewCount)
data_Nona3 <- data_Nona3[is.na(data_Nona3$viewCount)==FALSE,]
cor(data_Nona3,method="pearson")

set.seed(1434)
partition2 <- createDataPartition(data_Nona3$viewCount, p=0.8, list=FALSE)
training2 <- data_Nona3[ partition2, ]
testing2 <- data_Nona3[ -partition2, ]

fit3 <- lm(formula = training2$viewCount ~  
       training2$subscriberCount+ training2$commentCount + training2$videoCount, data = training2)

summary(fit3)

```

## Are the like and dislike important for our analysis?

In order to find if both like and dislike are important characteristics for our analysis; I will take some samples of them in order to create with other model another dataset that it will analyze with the previous method. 

```{r pressure}
data_likes <- data_without_id[is.na(data_without_id$likeCount)==FALSE,]
data_likes <- data_likes[,-c(4,5)]
data_likes[is.na(data_likes$commentCount),1] <- 444
data_likes[is.na(data_likes$viewCount),4] <- 162779
cor(data_likes,method="pearson")

#Multiple R-squared:  0.3826,	Adjusted R-squared:  0.3826 
likes_fit <- lm(formula = data_likes$likeCount ~  
       data_likes$viewCount , data = data_likes)
summary(likes_fit)

#Multiple R-squared:  0.5354,	Adjusted R-squared:  0.5351 
likes_fit <- lm(formula = data_likes$likeCount ~  
       data_likes$viewCount +data_likes$commentCount + data_likes$dislikeCount, data = data_likes)
summary(likes_fit)
```

```{r pressure}

prediction <- predict(likes_fit, newdata=data_without_id[is.na(data_without_id$likeCount)==FALSE,])
data_without_id_2 <- data_without_id
summary(data_without_id_2)
prediction <- predict(likes_fit, newdata=data_without_id_2[is.na(data_without_id_2$likeCount)==TRUE,-c(4,5)])
summary(data_without_id_2)


```




