---
title: "Titanic"
author: "Christian Urcuqui"
date: "23 de abril de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# spanish


** Table of Contents**


* [Introduccion](#introduccion)
* [Pregunta o objetivo](#pregunta-o-objetivo)
* [Exploracion](#exploration)
    * Cargar los datos
    * Cargar las librerias
    * Diccionario de datos
    * Transformacion de los datos
* [Entrenamiento](#entrenamiento)
* [Evaluacion](#evaluacion)

## Exploracion

### Cargar los datos

Vamos a cargar en memoria los archivos train.csv y test.csv, es decir, creamos y asignamdos dos dataframe

```{r data, echo=FALSE}

train <- read.csv(choose.files())
test <- read.csv(choose.files())

```


### librerias

```{r libraries}
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
```

### Diccionario de datos

Tomado y traducido de:
https://www.kaggle.com/c/titanic/data

		
| Variable  |Definition                                   |  Key                                          |
|-----------|---------------------------------------------|-----------------------------------------------|
| survival  | Survival                                    |  0 = No, 1 = Yes                              |
|  pclass   | Ticket class                                | 1 = 1st, 2 = 2nd, 3 = 3rd                     |
|  sex      | Age in years                                |                                               |
|  sibsp    |  # of siblings / spouses aboard the Titanic |                                               |
|  parch    |  # of parents / children aboard the Titanic |                                               |   
|  ticket   |  Ticket number                              |                                               | 
|  fare     |  Passenger fare                             |                                               |
|  cabin    |  Cabin number                               |                                               |
|  embarked |  Port of Embarkation                        |C = Cherbourg, Q = Queenstown, S = Southampton |


Variable Notes

pclass: A proxy for socio-economic status (SES)
1st = Upper
2nd = Middle
3rd = Lower

age: Age is fractional if less than 1. If the age is estimated, is it in the form of xx.5

sibsp: The dataset defines family relations in this way...
Sibling = brother, sister, stepbrother, stepsister
Spouse = husband, wife (mistresses and fiancés were ignored)

parch: The dataset defines family relations in this way...
Parent = mother, father
Child = daughter, son, stepdaughter, stepson
Some children travelled only with a nanny, therefore parch=0 for them.


### Transformacion de los datos

Ahora es importante verificar que los tipos de datos que sean compatibles con R y al contexto que estamos trabajando.

```{r tranform, echo=TRUE}

#training dataset

train$Survived <- as.factor(train$Survived)
train$Pclass <-as.factor(train$Pclass)
levels(train$Pclass) <-c(3,2,1)
train$Name <-as.character(train$Name)
train$Age <-as.integer(train$Age)
train$Ticket <- as.character(train$Ticket)

train$Cabin[train$Cabin ==""] <- NA

# testing dataset

test$Pclass <-as.factor(test$Pclass)
levels(test$Pclass) <-c(3,2,1)
test$Name <-as.character(test$Name)
test$Age <-as.integer(test$Age)
test$Ticket <- as.character(test$Ticket)
addNA()

# veamos si existen datos vacios

table(is.na(train))
# FALSE  TRUE 
# 10515   177 

# segun ello existen 177 datos vacios
summary(train)



```









# -----------------------------------------------------------------------------

# english

** Table of Contents**


* [Introduction](#introduction)
* [Question or Objective](#question-or-objective)
* [Exploration](#exploration)
    * Load data
    * Load libraries
    * Data transformation
* [Traning](#training)
* [Evaluation](#evaluation)


# Exploration

## libraries



```{r libraries}
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
```


# Input data files are available in the "../input/" directory.
# For example, running this (by clicking run or pressing Shift+Enter) will list the files in the input directory

system("ls ../input/train.csv")

# Any results you write to the current directory are saved as output.Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
